Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-26 Paper/ms.tex
Birth death reference

In this letter we introduce a trans-dimensional MCMC approach to inferring
$N$. When $N$ is treated as just another model parameter, we can obtain its
posterior distribution in a single run. Computing the expected RV signal from
a planet in an elliptical orbit can be slow. Therefore we use a lookup table
of precomputed orbits, allowing us to do $\sim 15000$ MCMC steps per second
per CPU core. The exploration is done using Diffusive Nested Sampling
\citep{dnest} which replaces the posterior distribution with an alternative
{\it mixture of constrained priors}, allowing mixing between separated modes.

@@

>>>>

In this letter we introduce a trans-dimensional birth-death MCMC approach
\citep{birthdeath} to inferring $N$.
When $N$ is treated as just another model parameter, we can obtain its
posterior distribution in a single run. Computing the expected RV signal from
a planet in an elliptical orbit can be slow. Therefore we use a lookup table
of precomputed orbits, allowing us to do $\sim 15000$ MCMC steps per second
per CPU core. The exploration is done using Diffusive Nested Sampling
\citep{dnest} which replaces the posterior distribution with an alternative
{\it mixture of constrained priors}, allowing mixing between separated modes.

@@

\bibitem[Stephens(2000)]{birthdeath} Stephens, M., 2000, ``Bayesian analysis of mixture models with an unknown number of components-an alternative to reversible jump methods.'', Annals of Statistics, 40-74.
